---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

In this report, I will be analyzing the circulation trends of books in a library. The data is collected from the public library system of a metropolitan city over a period of five years, from 2017 to 2023. The library system has a vast collection of books, ranging from fiction, non-fiction, biographies, children's books, and many more. I have chosen to analyze the circulation trends of adult fiction books, children's books, and non-fiction books.

### Summary Information

The data collected from the library system shows that the circulation of adult fiction books has decreased steadily over the past five years, with a total circulation of 256,789 books in 2017 and only 193,456 books in 2020. On the other hand, the circulation of non-fiction books has increased from 164,238 books in 2016 to 196,847 books in 2023. The circulation of children's books has remained relatively stable over the past five years, with a total circulation of 307,815 books in 2017 and 312,494 books in 2023. The library system had a total circulation of 728,842 books in 2017, which increased to 702,797 books in 2023.

### The Dataset

The data used in this report was collected and published by the public library system of a metropolitan city. The data includes the number of books borrowed from the library for each year from 2017 to 2023. The data was collected for all types of books available in the library system, including fiction, non-fiction, children's books, biographies, and others. The purpose of collecting this data was to analyze the circulation trends of different types of books in the library system. However, the data has some limitations, such as not accounting for the number of copies of each book available in the library, the duration of each book's availability, and the number of new books added to the collection each year.

### First Trends Over Time Chart

This chart shows the trend of checkouts over time from 2017 to 2023. There is a general downward trend in checkouts from all time in it, but has a rise in 2022. The highest number of checkouts was in 2018 (31456), while the lowest number was in 2020 (16039).

```{r, echo = FALSE, code = readLines("chart1_example.R")}
```

### Second Trends Over Time Chart

This chart shows the trend of checkouts over time from 2017 to 2023. There is a general downward trend in checkouts from all time in it, but has a rise in 2022. The highest number of checkouts was in 2018 (31456), while the lowest number was in 2020 (16039).

```{r, echo = FALSE, code = readLines("chart2_example.R")}
```

### Third Trends Over Time Chart

chart 3 shows the total number of checkouts for each material type in each year.This chart provides a visual representation of how the total number of checkouts for each material type has changed over time. It allows us to easily compare the popularity of different types of materials across different years. In this chart we can see that Audiobook, like ebook, has gradually increased with the years, while book, on the contrary, has recovered after the low tide of 2020 and 21. And videodisc is gradually weakening.

```{r, echo = FALSE, code = readLines("Chart_3.R")}
```
